Using Path-Dependent Types to Build Type-Safe JavaScript Foreign Function Interfaces

### 2014-01-10 papers/icwe14/icwe14.tex
blabla

However we observe that, despite these languages are statically typed, their integration of the browser API either is not type safe or gives less expression power to developers. Indeed, integrating an API designed for a dynamically typed language into a statically typed language can be challenging. For instance, the \jscode{createElement} function return type depends on the value of the \jscode{String} parameter it is passed.

>>>>

However we observe that, despite these languages are statically typed, their integration of the browser API either is not type safe or gives less expression power to the developers. Indeed, integrating an API designed for a dynamically typed language into a statically typed language can be challenging. For instance, the \jscode{createElement(name)} function return type depends on the value of its \jscode{name} parameter: \jscode{createElement('div')} returns a \jscode{DivElement}, \jscode{createElement('input')} returns an \jscode{InputElement}, \emph{etc}. Existing languages expose this function by making it return an \jscode{Element} (the least upper bound of the types of all the possible returned values), though a more precise type could be known at compile-time. Another way to expose this function consists in exposing several functions, each one fixing the value of the \jscode{name} parameter along with its return type. The first solution is not type safe and the second solution does not scale.
